Containers and R: the Rockerverse and beyond

### 2019-10-07 manuscript.Rmd
Piece about r-online

- run code with Versions of R: https://srv.colinfay.me/r-online
- old R versions: https://github.com/rocker-org/rocker-versioned/issues/138
- [semantic version tags for Rocker](https://github.com/rocker-org/rocker-versioned/#version-tags)
- debugging memory problems across multiple versions: https://github.com/wch/r-debug
- cross-R testing: Show how you can run the same script in multiple R variants in containers (new contribution). Ideally the images should be created using `containerit` and controlled with `stevedore`/`docker`, i.e. via an R script.

>>>>

As with any other software, each new version of R comes with its share of changes. 
Some are breaking changes, some are not, but the fact is that running a piece of code in a given version might give different s from another version ; which, in some case, can be an issue when it comes to reproducibility.
For example, think about R random seed: starting with `R 3.6.0`, running `set.seed(2811); sample(1:1000, 2)` will not give the same result as if it was run inside an older version of R.
That might seem trivial, but all the code using the random number generator will not be exactly reproducible after this breaking change. 
Detecting this kind of behavior is the reason why the [r-online](https://github.com/ColinFay/ronline) app has been developped: available as a standalone NodeJS app or [online](https://srv.colinfay.me/r-online), this app was designed for historic exploration of R: with it, the user can compare a piece of code run in two separate versions of R. 
Internally, this app takes the piece of code written by the user, opens one or two docker instances with the given version of R, and returns the result to the user.

- old R versions: https://github.com/rocker-org/rocker-versioned/issues/138
- [semantic version tags for Rocker](https://github.com/rocker-org/rocker-versioned/#version-tags)
- debugging memory problems across multiple versions: https://github.com/wch/r-debug
- cross-R testing: Show how you can run the same script in multiple R variants in containers (new contribution). Ideally the images should be created using `containerit` and controlled with `stevedore`/`docker`, i.e. via an R script.
